A lottery model of density-dependent selection in evolutionary genetics

### 2017-05-08 manuscript.tex
latest

Thus, assuming that $d$ can evolve in this sense, $d_{ig}$ is either comparable to or greater than $1-d_i$. Yet $d_{ig}$ cannot be appreciably greater than $1-d_i$ for long, because selection will then strongly favor reductions in $d_g$ over increases in $b$, thereby bringing $d_{ig}$ closer to $1-d_i$. Thus, we expect selection on $b$ and $d$ to be of comparable strength in disturbed environments as well.

>>>>

Thus, assuming that $d$ can evolve in this sense, $d_{ig}$ is either comparable to or greater than $1-d_i$. Yet $d_{ig}$ cannot be appreciably greater than $1-d_i$ for long, because selection will then strongly favor reductions in $d_g$ over increases in $b$, thereby bringing $d_{ig}$ closer to $1-d_i$. Thus, if $b$ and $d$ are subject to long-term evolution subject to external degradation at comparable rates \citep{bertram_2017}, then we expect selection on $b$ and $d$ to be of comparable strength in disturbed environments as well.
